---
title: "create_all_inputs"
output: html_document
date: "2022-12-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(dplyr)
library(tidyr)
#library(lessR)
library(tidyverse)
#library(mobility)
library(ggsci)
library(cowplot)
library(tidyr)
library(truncnorm)
library(ggplot2)
library(ggrepel)

knitr::opts_chunk$set(echo = TRUE)

library(gdistance)
library(rjags)
library(mobility)
library(rgdal)
source("functions_sims_aim3.R")
library(rgeos)
set.seed(1031)

```

## Load Zambia shapefile

```{r}
## load shapefile
shp_zam = readOGR(dsn = "../Shapefiles/zmb_admbnda_adm2_dmmu_20201124.shp")
shp_zam$district_lower = tolower(shp_zam$ADM2_EN)

centroids = gCentroid(shp_zam, byid = TRUE)

dat_shp = shp_zam@data
centr <- SpatialPointsDataFrame(centroids, data= shp_zam@data)
centroids_SAdf <- as.data.frame(coordinates(centr))  
centroids_SAdf$ADM2 = dat_shp$ADM2_EN
```

## Load districts.full

This includes:   
- district and province names  
- population data  
- birth and death rates  
- MCV1 coverage through 2018  
- seropositivity estimates from ZAMPHIA (lower and upper bounds)  
- SIA2016 estimates

```{r}
districts.full = read.csv("../inputs/districts.full.csv") # full dataset
districts.full3 = read.csv("../inputs/districts.full3.csv") # restricted to those with CDRs
```

## Read in district density from census

```{r}
dat_dens = readxl::read_xlsx("../data/district_area_pop_115_per2019Census.xlsx")
dat_dens$lower_dist = tolower(dat_dens$Admin2_Label)
dat_dens = dat_dens %>% dplyr::select(lower_dist, Density)
# check how many are in district dataset
dat_dens = dat_dens %>% mutate(in_dt = ifelse(lower_dist %in% districts.full$district_map, 1, 0))
districts.full= merge(districts.full, dat_dens, by.x = "district_map", by.y = "lower_dist", all.x=TRUE)
# add classification of urban vs rural
ndola_dens = 528.103067
choma_dens = 48.904353
cutoff = (ndola_dens+choma_dens)/2
districts.full = districts.full %>% mutate(residence = ifelse(Density<cutoff, "choma", "ndola"))

districts.full3 = merge(districts.full3, dat_dens, by.x = "district_map", by.y = "lower_dist", all.x=TRUE)
districts.full3 = districts.full3 %>% mutate(residence = ifelse(Density<cutoff, "choma", "ndola")) # note this is identical to using 400ppl/m2 cutoff or 500ppl/m2 cutoff that WorldPop uses
```



## Set up initial conditions for full set of districts (115)

```{r}
n_years = 9

# measles cfr = mean projected cfr 2016 - 2030: 1·3% (0·4–3·7) (https://www.thelancet.com/journals/langlo/article/PIIS2214-109X(18)30537-0/fulltext) --- check - should change this for IFR?
measles_cfr = 0.013


# recovery rate after infection with covid - assume 1 because we're doing time steps ~ 1 generation time
wane_mat = 0.45 / 2  # check with amy about source / look around for it - the paper she gave is on rubella and varicella; divide by 2 because our time step is 2 weeks

# proportion for whom vaccine dose is effective
p_eff_V1r = 0.85  # first routine dose
p_eff_V2r = 0.97  # second routine dose
p_eff_V1c = 0.93  # first campaign dose


## pull deaths
deaths_rate_full = districts.full %>% dplyr::select(province_deaths) 
rownames(deaths_rate_full) = districts.full$district_map ## rate per 1000 per year

## pull births
births_rate_full = districts.full %>% dplyr::select(cbr_province)
rownames(births_rate_full) = districts.full$district_map ## rate per 1000 per year

## mcv1 coverage data; for nationwide, use unicef estimates: https://www.google.com/url?sa=t&rct=j&q=&esrc=s&source=web&cd=&ved=2ahUKEwilrMi06cP6AhWB6qQKHbQtBZMQFnoECB0QAQ&url=https%3A%2F%2Fdata.unicef.org%2Fwp-content%2Fuploads%2F2022%2F07%2Fzmb.pdf&usg=AOvVaw2Nfk2xSKyPbP60OOwmKNZF
mcv1_cov_full = districts.full %>% dplyr::select(mcv1_cov_2016, mcv1_cov_2017, mcv1_cov_2018)
# add nationwide estimates
mcv1_cov_full$nat2016 = 0.97
mcv1_cov_full$nat2017 = 0.96
mcv1_cov_full$nat2018 = 0.94
mcv1_cov_full$nat2019 = 0.93
mcv1_cov_full$nat2020 = 0.96
mcv1_cov_full$nat2021 = 0.90
mcv1_cov_full = mcv1_cov_full %>% mutate(mcv1_cov_2019 = mcv1_cov_2018 * nat2019 / nat2018)
mcv1_cov_full = mcv1_cov_full %>% mutate(mcv1_cov_2020 = mcv1_cov_2019 * nat2020 / nat2019)
mcv1_cov_full = mcv1_cov_full %>% mutate(mcv1_cov_2021 = mcv1_cov_2020 * nat2021 / nat2020)
rownames(mcv1_cov_full) = districts.full$district_map ## proportion coverage
# make into a time step dataframe
mcv1_cov_dat_full = matrix(NA, nrow = nrow(districts.full), ncol = n_years * 26)
mcv1_cov_dat_full[, 1:26] = (mcv1_cov_full$mcv1_cov_2016)    # year 2016
mcv1_cov_dat_full[, (1+26):(26*2)] = mcv1_cov_full$mcv1_cov_2017 # year 2017
mcv1_cov_dat_full[, (1+26*2):(26*3)] = mcv1_cov_full$mcv1_cov_2018 # year 2018
mcv1_cov_dat_full[, (1+26*3):(26*4)] = mcv1_cov_full$mcv1_cov_2019 # year 2019 - scale 2018 estimates by ratio of national estimates
mcv1_cov_dat_full[, (1+26*4):(26*5)] = mcv1_cov_full$mcv1_cov_2020 # year 2020 - scale 2019 estimates by ratio of national estimates
mcv1_cov_dat_full[, (1+26*5):(26*6)] = mcv1_cov_full$mcv1_cov_2021 # year 2021 - scale 2020 estimates by ratio of national estimates
mcv1_cov_dat_full[, (1+26*6):(26*7)] = mcv1_cov_full$mcv1_cov_2021 # year 2022
mcv1_cov_dat_full[, (1+26*7):(26*8)] = mcv1_cov_full$mcv1_cov_2021 # year 2023
mcv1_cov_dat_full[, (1+26*8):(26*9)] = mcv1_cov_full$mcv1_cov_2021 # year 2024
mcv1_cov_dat_full = as.data.frame(mcv1_cov_dat_full)
colnames(mcv1_cov_dat_full)[1:26] = sprintf("2016.%s", seq(1:26))
colnames(mcv1_cov_dat_full)[(1+26):(26*2)] = sprintf("2017.%s", seq(1:26))
colnames(mcv1_cov_dat_full)[(1+26*2):(26*3)] = sprintf("2018.%s", seq(1:26))
colnames(mcv1_cov_dat_full)[(1+26*3):(26*4)] = sprintf("2019.%s", seq(1:26))
colnames(mcv1_cov_dat_full)[(1+26*4):(26*5)] = sprintf("2020.%s", seq(1:26))
colnames(mcv1_cov_dat_full)[(1+26*5):(26*6)] = sprintf("2021.%s", seq(1:26))
colnames(mcv1_cov_dat_full)[(1+26*6):(26*7)] = sprintf("2022.%s", seq(1:26))
colnames(mcv1_cov_dat_full)[(1+26*7):(26*8)] = sprintf("2023.%s", seq(1:26))
colnames(mcv1_cov_dat_full)[(1+26*8):(26*9)] = sprintf("2024.%s", seq(1:26))
# cap maximum at 99%
mcv1_cov_dat_full[mcv1_cov_dat_full>0.99]=0.99
rownames(mcv1_cov_dat_full) = districts.full$district_map 

# mcv2 coverage --- scale mcv1 coverage by ratio between mcv2 and mcv1 (nationwide)
mcv2_cov_full = mcv1_cov_full %>% mutate(mcv2_nat_2016 = 0.58,
                               mcv2_nat_2017 = 0.64,
                               mcv2_nat_2018 = 0.65,
                               mcv2_nat_2019 = 0.66,
                               mcv2_nat_2020 = 0.74,
                               mcv2_nat_2021 = 0.81)
mcv2_cov_full = mcv2_cov_full %>% mutate(mcv2_cov_2016 = mcv1_cov_2016 * mcv2_nat_2016 / nat2016,
                               mcv2_cov_2017 = mcv1_cov_2017 * mcv2_nat_2017 / nat2017,
                               mcv2_cov_2018 = mcv1_cov_2018 * mcv2_nat_2018 / nat2018,
                               mcv2_cov_2019 = mcv1_cov_2019 * mcv2_nat_2019 / nat2019,
                               mcv2_cov_2020 = mcv1_cov_2020 * mcv2_nat_2020 / nat2020,
                               mcv2_cov_2021 = mcv1_cov_2021 * mcv2_nat_2021 / nat2021)
# make into a time step dataframe
mcv2_cov_dat_full = matrix(NA, nrow = nrow(districts.full), ncol = n_years * 26)
mcv2_cov_dat_full[, 1:26] = (mcv2_cov_full$mcv2_cov_2016)    # year 2016
mcv2_cov_dat_full[, (1+26):(26*2)] = mcv2_cov_full$mcv2_cov_2017 # year 2017
mcv2_cov_dat_full[, (1+26*2):(26*3)] = mcv2_cov_full$mcv2_cov_2018 # year 2018
mcv2_cov_dat_full[, (1+26*3):(26*4)] = mcv2_cov_full$mcv2_cov_2019 # year 2019 - scale 2018 estimates by ratio of national estimates
mcv2_cov_dat_full[, (1+26*4):(26*5)] = mcv2_cov_full$mcv2_cov_2020 # year 2020 - scale 2019 estimates by ratio of national estimates
mcv2_cov_dat_full[, (1+26*5):(26*6)] = mcv2_cov_full$mcv2_cov_2021 # year 2021 - scale 2020 estimates by ratio of national estimates
mcv2_cov_dat_full[, (1+26*6):(26*7)] = mcv2_cov_full$mcv2_cov_2021 # year 2022
mcv2_cov_dat_full[, (1+26*7):(26*8)] = mcv2_cov_full$mcv2_cov_2021 # year 2023
mcv2_cov_dat_full[, (1+26*8):(26*9)] = mcv2_cov_full$mcv2_cov_2021 # year 2024
mcv2_cov_dat_full = as.data.frame(mcv2_cov_dat_full)
colnames(mcv2_cov_dat_full)[1:26] = sprintf("2016.%s", seq(1:26))
colnames(mcv2_cov_dat_full)[(1+26):(26*2)] = sprintf("2017.%s", seq(1:26))
colnames(mcv2_cov_dat_full)[(1+26*2):(26*3)] = sprintf("2018.%s", seq(1:26))
colnames(mcv2_cov_dat_full)[(1+26*3):(26*4)] = sprintf("2019.%s", seq(1:26))
colnames(mcv2_cov_dat_full)[(1+26*4):(26*5)] = sprintf("2020.%s", seq(1:26))
colnames(mcv2_cov_dat_full)[(1+26*5):(26*6)] = sprintf("2021.%s", seq(1:26))
colnames(mcv2_cov_dat_full)[(1+26*6):(26*7)] = sprintf("2022.%s", seq(1:26))
colnames(mcv2_cov_dat_full)[(1+26*7):(26*8)] = sprintf("2023.%s", seq(1:26))
colnames(mcv2_cov_dat_full)[(1+26*8):(26*9)] = sprintf("2024.%s", seq(1:26))
rownames(mcv2_cov_dat_full) = districts.full$district_map 
mcv2_cov_dat_full[mcv2_cov_dat_full>0.99]=0.99

# SIA2016 coverage
sia2016_cov_full = districts.full %>% dplyr::select(sia2016)
rownames(sia2016_cov_full) = districts.full$district_map

## SIA 2020 coverage
sia2020_cov_full = districts.full %>% dplyr::select(PCES2020)
rownames(sia2020_cov_full) = districts.full$district_map ## proportion coverage
sia2020_cov_full$sia2020 = sia2020_cov_full$PCES2020 / 100

sia_cov_full = matrix(0, nrow = nrow(districts.full), ncol = n_years * 26)
sia_cov_full = as.data.frame(sia_cov_full)
colnames(sia_cov_full)[1:26] = sprintf("2016.%s", seq(1:26))
colnames(sia_cov_full)[(1+26):(26*2)] = sprintf("2017.%s", seq(1:26))
colnames(sia_cov_full)[(1+26*2):(26*3)] = sprintf("2018.%s", seq(1:26))
colnames(sia_cov_full)[(1+26*3):(26*4)] = sprintf("2019.%s", seq(1:26))
colnames(sia_cov_full)[(1+26*4):(26*5)] = sprintf("2020.%s", seq(1:26))
colnames(sia_cov_full)[(1+26*5):(26*6)] = sprintf("2021.%s", seq(1:26))
colnames(sia_cov_full)[(1+26*6):(26*7)] = sprintf("2022.%s", seq(1:26))
colnames(sia_cov_full)[(1+26*7):(26*8)] = sprintf("2023.%s", seq(1:26))
colnames(sia_cov_full)[(1+26*8):(26*9)] = sprintf("2024.%s", seq(1:26))
rownames(sia_cov_full) = districts.full$district_map 
sia_cov_full$`2016.18` = sia2016_cov_full$sia2016
sia_cov_full$`2020.18` = sia2020_cov_full$sia2020

## pull population - use from districts.full2
pop_dat_full = districts.full %>% dplyr::select(province_2018, district_2018, pop_2016:pop_2019, growth_rate)
# start in 2016
pop_mat_full = matrix(NA, nrow = nrow(pop_dat_full), ncol = n_years * 26)
pop_mat_full[, 1:26] = (pop_dat_full$pop_2016)    # year 2016
pop_mat_full[, (1+26):(26*2)] = pop_dat_full$pop_2017 # year 2017
pop_mat_full[, (1+26*2):(26*3)] = pop_dat_full$pop_2018 # year 2018
pop_mat_full[, (1+26*3):(26*4)] = pop_dat_full$pop_2019 # year 2019
pop_mat_full[, (1+26*4):(26*5)] = pop_dat_full$pop_2019 * pop_dat_full$growth_rate # year 2020
pop_mat_full[, (1+26*5):(26*6)] = pop_dat_full$pop_2019 * (pop_dat_full$growth_rate)^2 # year 2021
pop_mat_full[, (1+26*6):(26*7)] = pop_dat_full$pop_2019 * (pop_dat_full$growth_rate)^3 # year 2022
pop_mat_full[, (1+26*7):(26*8)] = pop_dat_full$pop_2019 * (pop_dat_full$growth_rate)^4 # year 2023
pop_mat_full[, (1+26*8):(26*9)] = pop_dat_full$pop_2019 * (pop_dat_full$growth_rate)^5 # year 2024
pop_mat_full = as.data.frame(pop_mat_full)
colnames(pop_mat_full)[1:26] = sprintf("2016.%s", seq(1:26))
colnames(pop_mat_full)[(1+26):(26*2)] = sprintf("2017.%s", seq(1:26))
colnames(pop_mat_full)[(1+26*2):(26*3)] = sprintf("2018.%s", seq(1:26))
colnames(pop_mat_full)[(1+26*3):(26*4)] = sprintf("2019.%s", seq(1:26))
colnames(pop_mat_full)[(1+26*4):(26*5)] = sprintf("2020.%s", seq(1:26))
colnames(pop_mat_full)[(1+26*5):(26*6)] = sprintf("2021.%s", seq(1:26))
colnames(pop_mat_full)[(1+26*6):(26*7)] = sprintf("2022.%s", seq(1:26))
colnames(pop_mat_full)[(1+26*7):(26*8)] = sprintf("2023.%s", seq(1:26))
colnames(pop_mat_full)[(1+26*8):(26*9)] = sprintf("2024.%s", seq(1:26))
rownames(pop_mat_full) = districts.full$district_map 

# population starting in the maternal compartment - suppose it's something like children 0 - 3 months
# based on 2010 census, 2020 projection: children 0 - 5 = 17.5%
# assume children 0-3 months make up a little over 1/4 of 1/5 of 17.5% = 0.00875 of population
prop_mat = 0.00875

N0_full = pop_mat_full$`2016.1`  # total population 
M0_full = N0_full*prop_mat    # maternal compartment

# for susceptibles - pass in N0_full, plus lower, upper, and mean seroprev
lower_S0 = districts.full$lowerseroprev.pop.2016
upper_S0 = districts.full$upperseroprev.pop.2016
mean_S0 = districts.full$meanseroprev.pop.2016
S0_full = data.frame(lower_S0 = lower_S0,
                     upper_S0 = upper_S0,
                     mean_S0 = mean_S0)# susceptible compartment

# infectious individuals
I0_full = rep(0, length(N0_full))
lusaka_row = which(rownames(pop_mat_full)=="lusaka") # get rowname for Lusaka district
I0_full[lusaka_row] = c(10)

V1R0_full = rep(0, length(N0_full))
V20_full = rep(0, length(N0_full))
V1C0_full = rep(0, length(N0_full))


incid_deaths0 = rep(0, length(N0_full))

mob_data_prob_full = readRDS("outputs/feb11/M_CDR_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_prob_full)){
  mob_data_prob_full[[i]] = mob_data_prob_full[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}

#initial_conditions_full = data.frame(M0 = M0_full, S0 = S0_full , I0 = I0_full, V1R0 = V1R0_full, V1C0 = V1C0_full, V20 = V20_full, incid_deaths0 = incid_deaths0,  N0 = N0_full)
initial_conditions_full = data.frame(M = M0_full, S = S0_full , I0 = I0_full, V1R0 = V1R0_full, V1C0 = V1C0_full, V20 = V20_full, incid_deaths0 = incid_deaths0,  N0 = N0_full)

```

Introduction matrix
```{r}
# introduction matrix
lusaka_row_full = which(rownames(pop_mat_full)=="lusaka") # get rowname for Lusaka district

intro_mat_full = matrix(0, nrow = nrow(pop_dat_full), ncol = n_years * 26)
intro_mat_full[lusaka_row_full,] = c(rep(c(5, 0), ncol(intro_mat_full)/2))
intro_mat_full = as.data.frame(intro_mat_full)
rownames(intro_mat_full) = rownames(pop_mat_full)

```

Introduction matrix for Lunte, Chirundu, and Mafinga
```{r}
# introduction matrix
lunte_row_full = which(rownames(pop_mat_full)=="lunte district") # get rowname for Lusaka district
chirundu_row_full = which(rownames(pop_mat_full)=="chirundu") # get rowname for Chirundu district
mafinga_row_full = which(rownames(pop_mat_full)=="mafinga") # get rowname for Mafinga district


intro_mat_full_outbreak = matrix(0, nrow = nrow(pop_dat_full), ncol = n_years * 26)
intro_mat_full_outbreak[lunte_row_full,1] = 5
intro_mat_full_outbreak[chirundu_row_full,1] = 10
intro_mat_full_outbreak[mafinga_row_full,1] = 5

intro_mat_full_outbreak = as.data.frame(intro_mat_full_outbreak)
rownames(intro_mat_full_outbreak) = rownames(pop_mat_full)

```

Introduction matrix for Choma and Ndola
```{r}
# introduction matrix
choma_row_full = which(rownames(pop_mat_full)=="choma") 
ndola_row_full = which(rownames(pop_mat_full)=="ndola") 

intro_mat_full_choma_ndola = matrix(0, nrow = nrow(pop_dat_full), ncol = n_years * 26)
intro_mat_full_choma_ndola[choma_row_full,1] = 5
intro_mat_full_choma_ndola[ndola_row_full,1] = 5

intro_mat_full_choma_ndola = as.data.frame(intro_mat_full_choma_ndola)
rownames(intro_mat_full_choma_ndola) = rownames(pop_mat_full)

```
## Set up initial conditions for set of districts with CDRs (107)

```{r}
pop_dat = districts.full3 %>% dplyr::select(province_2018, district_2018, pop_2016:pop_2019, growth_rate)

pop_mat = pop_mat_full %>% filter(rownames(pop_mat_full) %in% districts.full3$district_map)
sia_cov = sia_cov_full %>% filter(rownames(sia_cov_full) %in% districts.full3$district_map)
deaths_rate = deaths_rate_full %>% filter(rownames(deaths_rate_full) %in% districts.full3$district_map)
births_rate = births_rate_full %>% filter(rownames(births_rate_full) %in% districts.full3$district_map)
mcv1_cov_dat = mcv1_cov_dat_full %>% filter(rownames(mcv1_cov_dat_full) %in% districts.full3$district_map)
mcv2_cov_dat = mcv2_cov_dat_full %>% filter(rownames(mcv2_cov_dat_full) %in% districts.full3$district_map)


N0 = pop_mat$`2016.1`  # total population 
M0 = N0*prop_mat    # maternal compartment
lower_S0 = districts.full3$lowerseroprev.pop.2016
upper_S0 = districts.full3$upperseroprev.pop.2016
mean_S0 = districts.full3$meanseroprev.pop.2016
S0_short = data.frame(lower_S0 = lower_S0,
                     upper_S0 = upper_S0,
                     mean_S0 = mean_S0)# susceptible compartment

# infectious individuals
I0 = rep(0, length(N0))
lusaka_row = which(rownames(pop_mat)=="lusaka") # get rowname for Lusaka district
I0[lusaka_row] = c(10)

# for now, set vaccinated compartments to 0 - though should probably have some people in them to start with
V1R0 = rep(0, length(N0))
V20 = rep(0, length(N0))
V1C0 = rep(0, length(N0))

#R0 = N0 - (M0 + S0 +I0 + V1R0+ V1C0+ V20+ V1C0)  # recovered

incid_deaths0 = rep(0, length(N0))


```

```{r}
# introduction matrix
intro_mat = intro_mat_full %>% filter(rownames(intro_mat_full) %in% districts.full3$district_map)

intro_mat_outbreak = intro_mat_full_outbreak %>% filter(rownames(intro_mat_full_outbreak) %in% districts.full3$district_map)

intro_mat_choma_ndola = intro_mat_full_choma_ndola %>% filter(rownames(intro_mat_full_choma_ndola) %in% districts.full3$district_map)
```

# # parameters
```{r}
t = n_years * 26 # 26 two-weeks in a year
Ncomp = 1
beta0 = 15
beta1 = 0.3

gamma = 1
beta_values = beta0 * (1 + beta1*cos(2*pi*seq(0,1,length=26)))
season_index = rep(1:26, n_years)

alpha = 0.975

delta.t = 1

# assume that average age at which people are moving from M to S is 1 / 0.45
# assume first dose of routine is at 9 months
# then time to MR1 is (9 - 1/0.45)
wane_prob = 0.45
MR1_time = (9 - 1/(wane_prob)) * 2  ## about 13 weeks
# MR2 time is at 18 months; so time from MR1 to MR2 is (18 - 9) = 9 months
MR2_time = (18 - 9) * 2

n_sims = 100
```

## Starting just at 2020 SIA campaign

```{r}
intro_mat_2020_full = intro_mat_full[, 121:234] 
intro_mat_2020 = intro_mat[, 121:234]


# try seeding introduction just in lusaka, 10 cases on first time step
intro_mat_2020[intro_mat_2020>0]=0  
intro_mat_2020[lusaka_row,1]=10

intro_mat_2020_full[intro_mat_2020_full>0]=0  
intro_mat_2020_full[lusaka_row_full,1]=10


```


Introduction matrix - outbreak-like: Lunte, Chirundu, and Mafinga




```{r}
# update population matrix
pop_mat2020_2 = pop_mat %>% dplyr::select("2020.17":"2021.26")

# update parameters
mcv1_cov_dat[mcv1_cov_dat>0.99]=0.99
mcv1_cov_dat2020_2 = mcv1_cov_dat %>% dplyr::select("2020.17":"2021.26")
mcv2_cov_dat[mcv2_cov_dat>0.99]=0.99
mcv2_cov_dat2020_2 = mcv2_cov_dat %>% dplyr::select("2020.17":"2021.26")
sia_cov2020_2 = sia_cov %>% dplyr::select("2020.17":"2021.26")
intro_mat2020_2 = intro_mat_2020[, 1:36] 
intro_mat2020_outbreak = intro_mat_outbreak[, 1:36]

intro_mat2020_outbreak_full = intro_mat_full_outbreak[, 1:36]


sd.dw.val = 0.01

t_2 = 36
```

# Intro matrix - seed in Choma and Ndola
```{r}
intro_mat2020_2 = intro_mat_2020[, 1:36] 
intro_mat2020_outbreak = intro_mat_outbreak[, 1:36]

intro_mat2020_outbreak_full = intro_mat_full_outbreak[, 1:36]


intro_mat_outbreak = intro_mat_full_outbreak %>% filter(rownames(intro_mat_full_outbreak) %in% districts.full3$district_map)

```

## Set up SIA three months in - target provinces with introductions (Lusaka, Northern, Eastern)

```{r}
# assume 
SIA_intros = districts.full %>% dplyr::select(lower_dist, district_map, province_2018) %>% mutate(SIA = ifelse(province_2018 %in% c("Lusaka", "Northern", "Eastern"), 1, 0))
SIA_intros = SIA_intros %>% filter(SIA==1)
dists_w_SIA = SIA_intros$district_map

sia_wintros_mat2020 = sia_cov2020_2
sia_wintros_mat2020[dists_w_SIA, "2020.20"] = 0.95

sia_cov2020_2_full = sia_cov_full %>% dplyr::select("2020.17":"2021.26")
sia_wintros_mat2020_full = sia_cov2020_2_full
sia_wintros_mat2020_full[dists_w_SIA, "2020.20"] = 0.95
```

## Set up initial conditions where there's much more even susceptibility across districts
```{r}
# for susceptibles - pass in N0_full, plus lower, upper, and mean seroprev
mean_S0 = runif(n = length(districts.full$upperseroprev.pop.2016), min = 0.83, max = 0.85)
lower_S0 = mean_S0 - 0.1
upper_S0 = mean_S0 + 0.1
S0_full_su = data.frame(lower_S0 = lower_S0,
                     upper_S0 = upper_S0,
                     mean_S0 = mean_S0)# susceptible compartment
incid_deaths0 = rep(0, length(N0_full))


initial_conditions_full_su = data.frame(M = M0_full, S = S0_full_su , I0 = I0_full, V1R0 = V1R0_full, V1C0 = V1C0_full, V20 = V20_full, incid_deaths0 = incid_deaths0,  N0 = N0_full)


```
