---
title: "Simulations_aim3"
output: html_document
date: "2023-02-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("functions_sims_aim3.R")
```

## Run set_up_ICs_aim3.Rmd first to set up initial conditions

# Seed 10 cases in Lusaka at time 0 only

## Scenario A - CDR departure, CDR diffusion

```{r}
# no introductions other than seeding first 10 people in lusaka
n_sims = 100

# update population matrix
pop_mat2020_2_full = pop_mat_full %>% dplyr::select("2020.17":"2021.26")

# update parameters
mcv1_cov_dat2020_2_full = mcv1_cov_dat_full %>% dplyr::select("2020.17":"2021.26")
mcv2_cov_dat2020_2_full = mcv2_cov_dat_full %>% dplyr::select("2020.17":"2021.26")
sia_cov2020_2_full = sia_cov_full %>% dplyr::select("2020.17":"2021.26")
intro_mat2020_2_full = intro_mat_2020_full[, 1:36] 


t_2 = 36

parameters_sc2_full = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_prob_full, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_2_full)


run_scA = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_full)
write.csv(run_scA, "results/run_scA.csv")

out_A = plots_post_run(runs_output = run_scA, 
                                    time_max = 36)

```

## Scenario B - CDRwDHS departure, CDR diffusion

```{r}
# update mobility matrix
mob_data_CDRwDHS_CDR = readRDS("outputs/feb11/M_CDRwDHS_CDR_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_CDRwDHS_CDR)){
  mob_data_CDRwDHS_CDR[[i]] = mob_data_CDRwDHS_CDR[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullB = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_CDRwDHS_CDR, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_2_full)


run_scB = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullB)
write.csv(run_scB, "results/run_scB.csv")

out_B = plots_post_run(runs_output = run_scB, 
                                    time_max = 36)

```


## Scenario C - FB departure, FB diffusion

```{r}
# update mobility matrix
mob_data_FB = readRDS("outputs/feb11/M_FB_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_FB)){
  mob_data_FB[[i]] = mob_data_FB[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullC = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_FB, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_2_full)


run_scC = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullC)
write.csv(run_scC, "results/run_scC.csv")

out_C = plots_post_run(runs_output = run_scC, 
                                    time_max = 36)

```


## Scenario D - FBwDHS departure, FB diffusion

```{r}
# update mobility matrix
mob_data_FBwDHS_FB = readRDS("outputs/feb11/M_FBwDHS_FB_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_FBwDHS_FB)){
  mob_data_FBwDHS_FB[[i]] = mob_data_FBwDHS_FB[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullD = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_FBwDHS_FB, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_2_full)


run_scD = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullD)
write.csv(run_scD, "results/run_scD.csv")

out_D = plots_post_run(runs_output = run_scD, 
                                    time_max = 36)

```



## Scenario E - TS departure, TS diffusion

```{r}
# update mobility matrix
mob_data_TS = readRDS("outputs/feb11/M_TS_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_TS)){
  mob_data_TS[[i]] = mob_data_TS[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullE = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_TS, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_2_full)


run_scE = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullE)
write.csv(run_scE, "results/run_scE.csv")

out_E = plots_post_run(runs_output = run_scE, 
                                    time_max = 36)

```






## Scenario F - FB departure, FB w TS prior diffusion

```{r}
# update mobility matrix
mob_data_FB_FBwTS = readRDS("outputs/feb11/M_FBwTSpr_FB_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_FB_FBwTS)){
  mob_data_FB_FBwTS[[i]] = mob_data_FB_FBwTS[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullF = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_FB_FBwTS, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_2_full)


run_scF = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullF)
write.csv(run_scF, "results/run_scF.csv")
```







## Scenario G - Pooled raw departure, CDR  diffusion

```{r}
# update mobility matrix
mob_data_pooled_CDR = readRDS("outputs/feb11/M_pool_CDR_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_pooled_CDR)){
  mob_data_pooled_CDR[[i]] = mob_data_pooled_CDR[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullG = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_pooled_CDR, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_2_full)


run_scG = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullG)
write.csv(run_scG, "results/run_scG.csv")
```










## Scenario H - Pooled wt departure, CDR diffusion

```{r}
# update mobility matrix
mob_data_pooled_wt_CDR = readRDS("outputs/feb11/M_pool_wt_CDR_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_pooled_wt_CDR)){
  mob_data_pooled_wt_CDR[[i]] = mob_data_pooled_wt_CDR[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullH = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_pooled_wt_CDR, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_2_full)


run_scH = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullH)
write.csv(run_scH, "results/run_scH.csv")
```






## Scenario I - DHS departure, TS diffusion

```{r}
# update mobility matrix
mob_data_DHS_TS = readRDS("outputs/feb11/M_DHS_TS_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_DHS_TS)){
  mob_data_DHS_TS[[i]] = mob_data_DHS_TS[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullI = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_DHS_TS, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_2_full)


run_scI = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullI)
write.csv(run_scI, "results/run_scI.csv")
```








## Scenario J - DHS departure, FB diffusion

```{r}
# update mobility matrix
mob_data_DHS_FB = readRDS("outputs/feb11/M_DHS_FB_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_DHS_FB)){
  mob_data_DHS_FB[[i]] = mob_data_DHS_FB[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullJ = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_DHS_FB, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_2_full)


run_scJ = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullJ)
write.csv(run_scJ, "results/run_scJ.csv")
```



## Scenario K - DHS departure, CDR diffusion

```{r}
# update mobility matrix
mob_data_DHS_CDR = readRDS("outputs/feb11/M_DHS_CDR_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_DHS_CDR)){
  mob_data_DHS_CDR[[i]] = mob_data_DHS_CDR[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullK = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_DHS_CDR, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_2_full)


run_scK = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullK)
write.csv(run_scK, "results/run_scK.csv")
```








## Scenario L - Pooled raw departure, FB diffusion

```{r}
# update mobility matrix
mob_data_pooled_FB = readRDS("outputs/feb11/M_pool_FB_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_pooled_FB)){
  mob_data_pooled_FB[[i]] = mob_data_pooled_FB[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullL = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_pooled_FB, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_2_full)


run_scL = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullL)
write.csv(run_scL, "results/run_scL.csv")
```









## Scenario M - Pooled raw departure, TS diffusion

```{r}
# update mobility matrix
mob_data_pooled_TS = readRDS("outputs/feb11/M_pool_TS_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_pooled_TS)){
  mob_data_pooled_TS[[i]] = mob_data_pooled_TS[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullM = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_pooled_TS, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_2_full)


run_scM = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullL)
write.csv(run_scM, "results/run_scM.csv")
```











# Seed 10 cases in Ndola and 10 cases in Choma at time 0 only

## Scenario A - CDR departure, CDR diffusion

```{r}
# no introductions other than seeding first 10 people in lusaka
n_sims = 100

# introduction in Choma and Ndola
intro_mat2020_choma_ndola_full = intro_mat_full_choma_ndola[, 1:36]




# update population matrix
pop_mat2020_2_full = pop_mat_full %>% dplyr::select("2020.17":"2021.26")

# update parameters
mcv1_cov_dat2020_2_full = mcv1_cov_dat_full %>% dplyr::select("2020.17":"2021.26")
mcv2_cov_dat2020_2_full = mcv2_cov_dat_full %>% dplyr::select("2020.17":"2021.26")
sia_cov2020_2_full = sia_cov_full %>% dplyr::select("2020.17":"2021.26")



t_2 = 36

parameters_sc2_full_cn = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_prob_full, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_choma_ndola_full)


run_scA_cn = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_full_cn)
write.csv(run_scA_cn, "results/run_scA_cn.csv")
```

## Scenario B - CDRwDHS departure, CDR diffusion

```{r}
# update mobility matrix
mob_data_CDRwDHS_CDR = readRDS("outputs/feb11/M_CDRwDHS_CDR_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_CDRwDHS_CDR)){
  mob_data_CDRwDHS_CDR[[i]] = mob_data_CDRwDHS_CDR[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullB_cn = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_CDRwDHS_CDR, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_choma_ndola_full)


run_scB_cn = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullB_cn)
write.csv(run_scB_cn, "results/run_scB_cn.csv")


```


## Scenario C - FB departure, FB diffusion

```{r}
# update mobility matrix
mob_data_FB = readRDS("outputs/feb11/M_FB_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_FB)){
  mob_data_FB[[i]] = mob_data_FB[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullC_cn = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_FB, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_choma_ndola_full)


run_scC_cn = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullC_cn)
write.csv(run_scC_cn, "results/run_scC_cn.csv")

```


## Scenario D - FBwDHS departure, FB diffusion

```{r}
# update mobility matrix
mob_data_FBwDHS_FB = readRDS("outputs/feb11/M_FBwDHS_FB_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_FBwDHS_FB)){
  mob_data_FBwDHS_FB[[i]] = mob_data_FBwDHS_FB[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullD_cn = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_FBwDHS_FB, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_choma_ndola_full)


run_scD_cn = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullD_cn)
write.csv(run_scD_cn, "results/run_scD_cn.csv")

```



## Scenario E - TS departure, TS diffusion

```{r}
# update mobility matrix
mob_data_TS = readRDS("outputs/feb11/M_TS_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_TS)){
  mob_data_TS[[i]] = mob_data_TS[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullE_cn = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_TS, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_choma_ndola_full)


run_scE_cn = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullE_cn)
write.csv(run_scE_cn, "results/run_scE_cn.csv")

```





## Scenario F - FB departure, FB with TS prior diffusion

```{r}
# update mobility matrix
mob_data_FB_FBwTS = readRDS("outputs/feb11/M_FBwTSpr_FB_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_FB_FBwTS)){
  mob_data_FB_FBwTS[[i]] = mob_data_FB_FBwTS[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullF_cn = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_FB_FBwTS, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_choma_ndola_full)


run_scF_cn = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullF_cn)
write.csv(run_scF_cn, "results/run_scF_cn.csv")

```


## Scenario G - Pooled raw departure, CDR diffusion

```{r}
# update mobility matrix
mob_data_pool_CDR = readRDS("outputs/feb11/M_pool_CDR_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_pool_CDR)){
  mob_data_pool_CDR[[i]] = mob_data_pool_CDR[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullG_cn = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_pool_CDR, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_choma_ndola_full)


run_scG_cn = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullG_cn)
write.csv(run_scG_cn, "results/run_scG_cn.csv")

```





## Scenario H - Pooled  departure w DHS, CDR diffusion

```{r}
# update mobility matrix
mob_data_pool_wt_CDR_full = readRDS("outputs/feb11/M_pool_wt_CDR_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_pool_wt_CDR_full)){
  mob_data_pool_wt_CDR_full[[i]] = mob_data_pool_wt_CDR_full[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullH_cn = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_pool_wt_CDR_full, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_choma_ndola_full)


run_scH_cn = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullH_cn)
write.csv(run_scH_cn, "results/run_scH_cn.csv")

```





## Scenario I - DHS departure, TS diffusion

```{r}
# update mobility matrix
mob_data_DHS_TS = readRDS("outputs/feb11/M_DHS_TS_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_DHS_TS)){
  mob_data_DHS_TS[[i]] = mob_data_DHS_TS[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullI_cn = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_DHS_TS, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_choma_ndola_full)


run_scI_cn = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullI_cn)
write.csv(run_scI_cn, "results/run_scI_cn.csv")

```





## Scenario J - DHS departure, FB diffusion

```{r}
# update mobility matrix
mob_data_DHS_FB = readRDS("outputs/feb11/M_DHS_FB_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_DHS_FB)){
  mob_data_DHS_FB[[i]] = mob_data_DHS_FB[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullJ_cn = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_DHS_FB, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_choma_ndola_full)


run_scJ_cn = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullJ_cn)
write.csv(run_scJ_cn, "results/run_scJ_cn.csv")

```





## Scenario K - DHS departure, CDR diffusion

```{r}
# update mobility matrix
mob_data_DHS_CDR = readRDS("outputs/feb11/M_DHS_CDR_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_DHS_CDR)){
  mob_data_DHS_CDR[[i]] = mob_data_DHS_CDR[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullK_cn = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_DHS_CDR, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_choma_ndola_full)


run_scK_cn = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullK_cn)
write.csv(run_scK_cn, "results/run_scK_cn.csv")

```

## Scenario L - Pooled raw departure, FB diffusion

```{r}
# update mobility matrix
mob_data_DHS_FB = readRDS("outputs/feb11/M_pool_FB_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_DHS_FB)){
  mob_data_DHS_FB[[i]] = mob_data_DHS_FB[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullL_cn = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_DHS_FB, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_choma_ndola_full)


run_scL_cn = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullL_cn)
write.csv(run_scL_cn, "results/run_scL_cn.csv")

```





## Scenario M - Pooled raw departure, TS diffusion

```{r}
# update mobility matrix
mob_data_DHS_TS = readRDS("outputs/feb11/M_pool_TS_full.rds")
# order in same way as the other initial conditions
for (i in 1:length(mob_data_DHS_TS)){
  mob_data_DHS_TS[[i]] = mob_data_DHS_TS[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
}


parameters_sc2_fullM_cn = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_DHS_TS, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_choma_ndola_full)


run_scM_cn = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullM_cn)
write.csv(run_scM_cn, "results/run_scM_cn.csv")

```

############### SENSITIVITY ANALYSIS - DIFFERENT R0 VALUES AND GENERATION TIMES ################

# change beta values -- divide by 4
```{r}
beta0_low = 15 / 4
beta1_low = 0.3

gamma = 1
beta_values_low = beta0_low * (1 + beta1_low*cos(2*pi*seq(0,1,length=26)))

parameters_sc2_full_low = parameters_sc2_full
parameters_sc2_full_low$beta_values = beta_values_low

```


## Scenario A - CDR departure, CDR diffusion

```{r}

run_scA_betalow = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_full_low)
write.csv(run_scA_betalow, "results/run_scA_betalow.csv")

out_A_betalow = plots_post_run(runs_output = run_scA_betalow, 
                                    time_max = 36)

```
## Scenario C - FB departure, FB diffusion

```{r}
parameters_sc2_fullC_betalow =parameters_sc2_fullC
parameters_sc2_fullC_betalow$beta_values = beta_values_low

run_scC_betalow = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullC_betalow)
write.csv(run_scC_betalow, "results/run_scC_betalow.csv")

out_C_betalow = plots_post_run(runs_output = run_scC_betalow, 
                                    time_max = 36)

```


## Scenario E - TS departure, TS diffusion

```{r}

parameters_sc2_fullE_betalow =parameters_sc2_fullE
parameters_sc2_fullE_betalow$beta_values = beta_values_low

run_scE_betalow = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullE_betalow)
write.csv(run_scE_betalow, "results/run_scE_betalow.csv")

out_E_betalow = plots_post_run(runs_output = run_scE_betalow, 
                                    time_max = 36)

```



# change beta values -- set to 2
```{r}
beta0_two = 15/2
beta1_low = 0.3

gamma = 1
beta_values_beta2 = beta0_two * (1 + beta1_low*cos(2*pi*seq(0,1,length=26)))

parameters_sc2_full_2 = parameters_sc2_full
parameters_sc2_full_2$beta_values = beta_values_beta2

```


## Scenario A - CDR departure, CDR diffusion

```{r}

run_scA_beta2 = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_full_2)
write.csv(run_scA_beta2, "results/run_scA_beta2.csv")

out_A_beta2 = plots_post_run(runs_output = run_scA_beta2, 
                                    time_max = 36)

```
rf## Scenario C - FB departure, FB diffusion

```{r}
parameters_sc2_fullC_beta2 =parameters_sc2_fullC
parameters_sc2_fullC_beta2$beta_values = beta_values_beta2

run_scC_beta2 = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullC_beta2)
write.csv(run_scC_beta2, "results/run_scC_beta2.csv")

out_C_beta2 = plots_post_run(runs_output = run_scC_beta2, 
                                    time_max = 36)

```


## Scenario E - TS departure, TS diffusion

```{r}

parameters_sc2_fullE_beta2 =parameters_sc2_fullE
parameters_sc2_fullE_beta2$beta_values = beta_values_beta2

run_scE_beta2 = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_sc2_fullE_beta2)
write.csv(run_scE_beta2, "results/run_scE_beta2.csv")

out_E_beta2 = plots_post_run(runs_output = run_scE_beta2, 
                                    time_max = 36)

```


## Sensitivity analysis - missed population approach
```{r}
t_2 = 36

name_files = dir("outputs/sensitivity")

#mob_data_temp = readRDS("outputs/sensitivity/M_CDR_delta1_theta1_omega1_1_omega2_1_p1.rds")
# original start: k = 3 (first two files not what we want for this)
start_k = 101
end_k = length(name_files)
for (k in start_k:end_k){
  mob_data_temp = readRDS(paste0("outputs/sensitivity/", name_files[3]))
  # order in same way as the other initial conditions
  for (i in 1:length(mob_data_temp)){
    mob_data_temp[[i]] = mob_data_temp[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
  }
  
  parameters_t1 = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_temp, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_2_full)
  
  
  run_sen1 = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_t1)
  
  write_name = paste0("outputs/sen/sens", k, ".csv")
  write.csv(run_sen1, write_name)
}
#write.csv(run_sen1, "results/sensitivity/run_sc1.csv")


```

```{r}

# check
sens3 = read.csv("outputs/sen/sens3.csv")
sens3_p = plots_post_run(runs_output = sens3, time_max = 36)

sens4 = read.csv("outputs/sen/sens4.csv")
sens4_p = plots_post_run(runs_output = sens4, time_max = 36)



```

## Sensitivity analysis - missed population approach -- more susceptible ICs
```{r}
t_2 = 36

name_files = dir("outputs/sensitivity")

#mob_data_temp = readRDS("outputs/sensitivity/M_CDR_delta1_theta1_omega1_1_omega2_1_p1.rds")
# original start: k = 3 (first two files not what we want for this)
start_k = 101
end_k = length(name_files)
for (k in start_k:end_k){
  mob_data_temp = readRDS(paste0("outputs/sensitivity/", name_files[3]))
  # order in same way as the other initial conditions
  for (i in 1:length(mob_data_temp)){
    mob_data_temp[[i]] = mob_data_temp[[i]][rownames(pop_mat_full), rownames(pop_mat_full)]
  }
  
  parameters_t1 = list(sd.dw.val = sd.dw.val, t = t_2, mob_data_prob = mob_data_temp, mcv1_cov_dat = mcv1_cov_dat2020_2_full, mcv2_cov_dat= mcv2_cov_dat2020_2_full, sia_cov = sia_cov2020_2_full, births_rate = births_rate_full, wane_mat = wane_mat, beta_values = beta_values, alpha = alpha, deaths_rate = deaths_rate_full, measles_cfr = measles_cfr, MR1_time = MR1_time, MR2_time = MR2_time, p_eff_V1r =p_eff_V1r, p_eff_V1c =p_eff_V1c, intro_mat = intro_mat2020_2_full)
  
  
  run_sen1 = multi_run(num_runs = n_sims, p_mat = pop_mat2020_2_full, ICs = initial_conditions_full, pars = parameters_t1)
  
  write_name = paste0("outputs/sen/sens", k, ".csv")
  write.csv(run_sen1, write_name)
}
#write.csv(run_sen1, "results/sensitivity/run_sc1.csv")


```

```{r}

# check
sens3 = read.csv("outputs/sen/sens3.csv")
sens3_p = plots_post_run(runs_output = sens3, time_max = 36)

sens4 = read.csv("outputs/sen/sens4.csv")
sens4_p = plots_post_run(runs_output = sens4, time_max = 36)



```
